Offshore Modeling - Manuscript Model

### 2020-02-18 2019_edits/R/offshore_analyses/final_analyses/Manuscript_Offshore_Modeling.Rmd
figure alterations

#packages
library(MASS)
library(here)
library(tidyverse)
library(knitr)
library(emmeans)
library(patchwork)
library(gridExtra)
library(broom)
library(statmod)
library(sf)
conflicted::conflict_prefer("select", "dplyr")
conflicted::conflict_prefer("filter", "dplyr")

#Format ggplot for rest of document
theme_set(theme_bw() + 
          theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(), 
            panel.border = element_rect(fill = NA),
            axis.text = element_text(size = 12, color = "black"),
            axis.title = element_text(size = 12, color = "black"),
            legend.text = element_text(size = 12, color = "black"),
            legend.background = element_rect(fill = NA))
          )

@@

year_plot <- year_sums %>% 
  mutate(survey_year = as.numeric(as.character(survey_year))) %>% 
  ggplot() +
    geom_col(aes(survey_year, `Mean Catch`), fill = "gray35") +
    geom_errorbar(aes(x = survey_year, 
                      ymin = catch_ymin,
                      ymax = catch_ymax),
                  size = .25) +
  geom_hline(yintercept = west_mean, 
             linetype = "dashed") +
  labs(x = NULL,
       y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))
  )

@@

year_foa <- year_sums %>% 
  mutate(survey_year = as.numeric(as.character(survey_year))) %>% 
  ggplot() +
    geom_col(aes(survey_year, `% Occurrence`)) +
    geom_hline(yintercept = west_foa, 
               linetype = "dashed") +
    scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
    labs(x = NULL, y = "Percent occurrence")

@@

#Summary Table
rs_summary %>%
  select(Region = region, Season, Stations, `Missing Obs`, `Mean Catch`, SD, Overdispersed) %>%
  knitr::kable()
```

@@

@@

@@

@@

```{r, fig.height=4}
rs_plot_2 <- rs_foa %>% 
  ggplot(aes(region, avg_percent_occurrence, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray70"), c("Summer", "Fall"))) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = NULL,
       y = "Percent occurrence") + 
  theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2))

@@

@@

@@

#Overall group means
panel_means <- seamap_west %>% 
  group_by(region, season) %>% 
  summarise(Mean_CPUE = mean(cpue_towspd))

#ggplot of standardized index of abundance
p <- best_mod_dat %>% 
  mutate(year_n = as.numeric(as.character(year_f))) %>% 
  ggplot(aes(year_n, response)) +
    geom_hline(data = panel_means, 
               aes(yintercept = Mean_CPUE), alpha = 0.5) +
    # geom_ribbon(aes(year_n, 
    #                 ymin = asymp.LCL, 
    #                 ymax = asymp.UCL), 
    #             fill = "gray80") +
    geom_line(aes(x = year_n, 
                  y = response, 
                  group = 1, 
                  col = "Predicted")) +
    geom_point(aes(x = year_n, 
                   y = response, 
                   col = "Predicted")) +
    # Observed Data
    geom_line(data = obs_timeline, 
            aes(x = survey_year, 
                y = Mean_CPUE, 
                group = region, 
                col = "Observed"), linetype = 2) +
    geom_point(data = obs_timeline, 
               aes(x = survey_year, 
                   y = Mean_CPUE, 
                   group = region, 
                   col = "Observed")) +
    #Theme changes
    #scale_color_grey(start = 0.35, end = 0.7) + 
    scale_color_manual(values = c("gray35", "royalblue")) + 
    labs(
      x = NULL, 
      y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))) +
  theme(legend.position = c(1, .98),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    legend.title = element_blank()) +
  facet_grid(season~region)
p

@@

ggplot() +
  geom_sf(data = szones, fill = NA) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  geom_text(data = sz_df, aes(long, lat, label = SZ), size = 3.5) +
  coord_sf(xlim = c(-98, -81), ylim = c(24, 31)) +
  labs(x = NULL, y = NULL)  +
  scale_y_continuous(breaks = c(25,30))
```

@@

```{r}
####  Sampling Effort  ####
ggplot() +
  geom_stars(data = effort_ras) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
  coord_sf(xlim = c(-98, -81), ylim = c(24, 31)) +
  scale_y_continuous(breaks = c(25,30)) +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_colorbar(title = "Total Sampling Effort (Stations)",
                               title.hjust = 0.5, 
                               title.position = "top",
                               barwidth = 10)) +
  theme(legend.position = "bottom", 
        legend.text = element_text(size  = 12), 
        legend.title = element_text(size = 12))
```

@@

####  CPUE  ####
ggplot() +
  geom_stars(data = cpue_ras) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
  coord_sf(xlim = c(-98, -81), ylim = c(24, 31)) +
  scale_y_continuous(breaks = c(25,30)) +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_colorbar(title = "Average Catch/Hectare",
                               title.hjust = 0.5, 
                               title.position = "top",
                               barwidth = 10)) +
  theme(legend.position = "bottom", 
        legend.text = element_text(size  = 12), 
        legend.title = element_text(size = 12))

@@

```{r}
####  Total Catch  ####
ggplot() +
  geom_stars(data = catch_ras) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
  coord_sf(xlim = c(-98, -81), ylim = c(24, 31)) +
  scale_y_continuous(breaks = c(25,30)) +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_colorbar(title = "Total C. sapidus Caught",
                               title.hjust = 0.5, 
                               title.position = "top",
                               barwidth = 10)) +
  theme(legend.position = "bottom", 
        legend.text = element_text(size  = 12), 
        legend.title = element_text(size = 12))

>>>>

#packages
library(ggspatial)
library(MASS)
library(here)
library(tidyverse)
library(knitr)
library(emmeans)
library(patchwork)
library(gridExtra)
library(broom)
library(statmod)
library(sf)

conflicted::conflict_prefer("select", "dplyr")
conflicted::conflict_prefer("filter", "dplyr")

#Format ggplot for rest of document
theme_set(theme_bw() + 
          theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(), 
            panel.border = element_rect(fill = NA),
            axis.text = element_text(size = 12, color = "black"),
            axis.title = element_text(size = 12, color = "black"),
            legend.text = element_text(size = 12, color = "black"),
            legend.background = element_rect(fill = NA),
            strip.text = element_text(size = 12, color = "black"))
          )

@@

year_plot <- year_sums %>% 
  mutate(survey_year = as.numeric(as.character(survey_year))) %>% 
  ggplot() +
    geom_col(aes(survey_year, `Mean Catch`), fill = "gray50") +
    geom_errorbar(aes(x = survey_year, 
                      ymin = catch_ymin,
                      ymax = catch_ymax),
                  size = .25) +
  geom_hline(yintercept = west_mean, 
             linetype = "dashed") +
  labs(x = NULL,
       y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))
  )

@@

year_foa <- year_sums %>% 
  mutate(survey_year = as.numeric(as.character(survey_year))) %>% 
  ggplot() +
    geom_col(aes(survey_year, `% Occurrence`), fill = "gray50") +
    geom_hline(yintercept = west_foa, 
               linetype = "dashed") +
    scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
    labs(x = NULL, y = "Percent occurrence")

@@

#Summary Table
rs_summary %>%
  select(Region = region, Season, Stations, `Missing Obs`, `Mean Catch`, SD, Overdispersed) %>%
  knitr::kable()

####  Full Gulf Summaries  ####
#Mean CPUE for the regions within each season
rs_summary_full <- seamap %>%
  filter(is.na(region)      == FALSE) %>%
  group_by(region, season) %>%
  summarise(Stations          = n(),
            `Missing Obs`     = sum(is.na(cpue_towspd)),
            `Mean Catch`      = mean(cpue_towspd, na.rm = T),
            `SD`              = sd(cpue_towspd, na.rm = T),
            `Var`             = var(cpue_towspd),
            `Overdispersed`   = ifelse(Var > `Mean Catch`, "yes", "no"),
            `Catch SE`        = sd(cpue_towspd, na.rm = T) / sqrt(Stations - `Missing Obs`)) %>%
    ungroup() %>%
    mutate(Season             = factor(season, levels = c("Summer", "Fall")),
           region             = factor(region,
                                       levels = c("Texas", "LA West", "MS Bight", "Florida")),
           #region             = fct_rev(region),
           catch_ymin         = `Mean Catch` - (2 * `Catch SE`),
           catch_ymax         = `Mean Catch` + (2 * `Catch SE`),
           catch_ymin         = ifelse(catch_ymin < 0, 0, catch_ymin)
    )
#Calaculate Annual average percent occurrence
rs_foa_full <- seamap %>% 
  group_by(survey_year, region, season) %>% 
  summarise(percent_occurrence = mean(crab_presence, na.rm = T)) %>% 
  group_by(region, season) %>% 
  summarise(nyears = n(),
            avg_percent_occurrence = mean(percent_occurrence, na.rm = T),
            po_se = sd(percent_occurrence, na.rm = T) / sqrt(nyears)) %>% 
    ungroup() %>%
    mutate(Season             = factor(season, levels = c("Summer", "Fall")),
           region             = factor(region, levels = c("Texas", "LA West", 
                                                          "MS Bight", "Florida")),
           occurrence_ymin    = avg_percent_occurrence - (2 * po_se),
           occurrence_ymax    = avg_percent_occurrence + (2 * po_se),
           occurrence_ymin    = ifelse(occurrence_ymin < 0, 0, occurrence_ymin),
           occurrence_ymax    = ifelse(occurrence_ymax > 1, 1, occurrence_ymax)
    )

@@

```{r west summs}

@@

```{r west fig, fig.height=4}

@@

```{r full fig, fig.height=4}

# Plot
rs_plot_3 <- rs_summary_full %>% 
  ggplot(aes(region, `Mean Catch`, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = catch_ymin,
                      ymax = catch_ymax),
                  position = "dodge", 
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray70"), c("Summer", "Fall"))) +
  labs(x = NULL,
       y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))) + 
  theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2))

rs_plot_3
```

@@

```{r west foa, fig.height=4}
rs_plot_2 <- rs_foa %>% 
  ggplot(aes(region, avg_percent_occurrence, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray70"), c("Summer", "Fall"))) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = NULL,
       y = "Percent occurrence") + 
  theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2))

@@

```{r full foa, fig.height=4}
rs_plot_4 <- rs_foa_full %>% 
  ggplot(aes(region, avg_percent_occurrence, fill = Season)) +
    geom_col(position = "dodge") +
    geom_errorbar(aes(ymin = occurrence_ymin,
                      ymax = occurrence_ymax),
                  position = "dodge",
                  size = .25) +
  scale_fill_manual(name = "", values = setNames(c("gray35", "gray70"), c("Summer", "Fall"))) +
  scale_y_continuous(labels = scales::percent, limits = c(0,1)) + 
  labs(x = NULL,
       y = "Percent occurrence") + 
  theme(
    legend.position = c(1, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2))

rs_plot_4
```

@@

rs_plot_full <- rs_plot_3 + theme(legend.position = "none")
rs_plot_full + rs_plot_4
```

@@

#Overall group means
panel_means <- seamap_west %>% 
  group_by(region, season) %>% 
  summarise(Mean_CPUE = mean(cpue_towspd)) %>% 
  ungroup() %>% 
  mutate(season = factor(season, levels = c("Summer", "Fall")),
         region = factor(region, levels = c("Texas", "LA West", "MS Bight")))

#ggplot of standardized index of abundance
p <- best_mod_dat %>% 
  mutate(year_n = as.numeric(as.character(year_f))) %>% 
  ggplot(aes(year_n, response)) +
    geom_ribbon(aes(year_n,
                    ymin = asymp.LCL,
                    ymax = asymp.UCL),
                fill = "gray80") +
    geom_line(aes(x = year_n, 
                  y = response, 
                  group = 1, 
                  col = "Predicted")) +
    geom_point(aes(x = year_n, 
                   y = response, 
                   col = "Predicted")) +
    # Observed Data
    geom_line(data = obs_timeline, 
            aes(x = survey_year, 
                y = Mean_CPUE, 
                group = region, 
                col = "Observed"), linetype = 2) +
    geom_point(data = obs_timeline, 
               aes(x = survey_year, 
                   y = Mean_CPUE, 
                   group = region, 
                   col = "Observed")) +
    #Group Means
    # geom_hline(data = panel_means, 
    #            aes(yintercept = Mean_CPUE), alpha = 0.5, linetype = 1, color = "darkred") +
    #Theme changes
    #scale_color_grey(start = 0.35, end = 0.7) + 
    scale_color_manual(values = c("royalblue", "black")) + 
    labs(
      x = NULL, 
      y = expression(paste("Mean CPUE (crabs ", ha^{-1},")"))) +
  theme(legend.position = c(1, .98),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(0, 6, 2, 2),
    legend.background = element_rect(fill = NA),
    legend.title = element_blank()) +
  facet_grid(season~region)
p

@@

ggplot() +
  geom_sf(data = szones, fill = NA) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  geom_text(data = sz_df, aes(long, lat, label = SZ), size = 3.5) +
  coord_sf(xlim = c(-98, -81), ylim = c(24, 31)) +
  labs(x = NULL, y = NULL)  +
  scale_y_continuous(breaks = c(25,30)) +
  annotation_north_arrow(
    height = unit(0.4, "in"),
    location = "bl", 
    which_north = "true", 
    pad_x = unit(0, "in"), 
    pad_y = unit(0, "in"),
    style = north_arrow_fancy_orienteering) +
  annotation_scale(
    pad_x = unit(0.5, "in"))
```

@@

```{r}
####  Sampling Effort  ####
ggplot() +
  geom_stars(data = effort_ras) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
  coord_sf(xlim = c(-98, -81), ylim = c(24, 31)) +
  scale_y_continuous(breaks = c(25,30)) +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_colorbar(title = "Total Sampling Effort (Stations)",
                               title.hjust = 0.5, 
                               title.position = "top",
                               barwidth = 10)) +
  theme(legend.position = "bottom", 
        legend.text = element_text(size  = 12), 
        legend.title = element_text(size = 12)) +
  annotation_north_arrow(
    height = unit(0.4, "in"),
    location = "bl", 
    which_north = "true", 
    pad_x = unit(0, "in"), 
    pad_y = unit(0, "in"),
    style = north_arrow_fancy_orienteering) +
  annotation_scale(
    pad_x = unit(0.5, "in"))
```

@@

####  CPUE  ####
ggplot() +
  geom_stars(data = cpue_ras) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
  coord_sf(xlim = c(-98, -81), ylim = c(24, 31)) +
  scale_y_continuous(breaks = c(25,30)) +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_colorbar(title = "Average Catch/Hectare",
                               title.hjust = 0.5, 
                               title.position = "top",
                               barwidth = 10)) +
  theme(legend.position = "bottom", 
        legend.text = element_text(size  = 12), 
        legend.title = element_text(size = 12)) +
  annotation_north_arrow(
    height = unit(0.4, "in"),
    location = "bl", 
    which_north = "true", 
    pad_x = unit(0, "in"), 
    pad_y = unit(0, "in"),
    style = north_arrow_fancy_orienteering) +
  annotation_scale(
    pad_x = unit(0.5, "in"))

@@

```{r}
####  Total Catch  ####
ggplot() +
  geom_stars(data = catch_ras) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  scale_fill_distiller(palette = "Spectral", na.value = "transparent") +
  coord_sf(xlim = c(-98, -81), ylim = c(24, 31)) +
  scale_y_continuous(breaks = c(25,30)) +
  labs(x = NULL, y = NULL) +
  guides(fill = guide_colorbar(title = "Total C. sapidus Caught",
                               title.hjust = 0.5, 
                               title.position = "top",
                               barwidth = 10)) +
  theme(legend.position = "bottom", 
        legend.text = element_text(size  = 12), 
        legend.title = element_text(size = 12)) +
  annotation_north_arrow(
    height = unit(0.4, "in"),
    location = "bl", 
    which_north = "true", 
    pad_x = unit(0, "in"), 
    pad_y = unit(0, "in"),
    style = north_arrow_fancy_orienteering) +
  annotation_scale(
    pad_x = unit(0.5, "in"))
